---
title: "PA1_template.Rmd"
author: "Marcos Melendez"
date: "11/27/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Show any code that is needed to load the data and process and transform

```{r fig.show= 'hide'}
activity <- read.csv("C:/Users/melen/Desktop/Exploratory Data Analysis//activity.csv", header = TRUE)

View(activity)

dim(activity)

str(activity)

summary(activity)
head(activity)
tail(activity)
```

# What is mean total number of steps taken per day?


```{r fig.show= 'hide'} 

total_number_of_steps <- with(activity, tapply(steps, as.factor(activity$date), sum, na.rm = T))


summary(total_number_of_steps)

filtered_steps <- activity[!is.na(activity$steps),]

```

```{r}
#Histogram
hist(total_number_of_steps, main = "Number of steps per day", xlab = "Total number of steps")

#Report the the mean and median of the total number of steps taken per day

summary(total_number_of_steps)
```

# What is the average daily activity pattern?

```{r}
mean_steps <- with(filtered_steps, tapply(steps, filtered_steps$interval, mean))

#mean_steps <- with(activity, tapply(steps, filtered_steps$interval, mean))

interval <- levels(as.factor(filtered_steps$interval))

plot(interval, mean_steps, type = "l", main = "Average number of steps", xlab = "interval", ylab = "Mean of steps")
```


# Imputing missing values
```{r}
length(filtered_steps$steps)
```

# Devise a strategy to fill all of the missing values in the data set

```{r fig.show= 'hide'}
missing_data <- activity[is.na(activity$steps),]

newdataset <- rbind(filtered_steps, missing_data)
table <- data.frame(mean_steps, interval)


```

# Are there differences in activity patterns between weekdays and weekends

library(ggplot2)

newdataset$days <- weekdays(as.Date(newdataset$date))


